HCI Draft Paper

### 2015-11-30 sigchi-latex-proceedings 2/draft-paper.tex
apparatus

\section{Methodology}
\section{Apparatus}

>>>>

\section{Methodology}
\section{Apparatus}
Two LG Nexus 5 phones were used as the apparatus for the experiment, one loaded with the stacked multitasking interface and the other with the non stacked interface. The stacked interface uses Android OS version 5.1 (Lollipop) while the non-stacked uses Android OS 4.4.4 (Kitkat). Both Android OS versions used were official Google releases and did not include any carrier or manufacturer modifications.

The Nexus 5 was released two years ago and has a 4.95 inch screen with a Snapdragon 800 Quad-Core processing chip. These specifications put it in the mid-range of current Android phones. We felt that using the Nexus 5 gives us a more accurate representation of what an average Android user would be using in the real world. This will reduce the bias of unfamiliarity and novelty when testing.
